The imprint of global magma oceans on exoplanet demographics

### 2022-12-03 src/tex/ms.tex
add plot comparing M-R relations of different cases

>>>>

\begin{figure}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/radiuscomparison.pdf}
        \caption{Mass-radius relationships for a water mass fraction of \wrr\ and different planet states: A) fully solid planets without magma oceans. B) planets with steam atmospheres. C) As B), but including the effect of water incorporation in the melt.}
        \label{fig:radiuscomparison}
    \end{centering}
\end{figure}

Figure~\ref{fig:radiuscomparison} shows the different mass-radius relations of the three cases for a fiducial water mass fraction of \wrr.
In general, steam atmospheres (case B) cause a significant radius increase, which is slightly reduced when water incorporation in the melt is allowed (case C).
